Verifying Demonstrations

### 2020-02-26 paper/related-work.tex
adds hobbits and Chaum to related work, updates tamarin text

>>>>

\textcite{DistanceBounding} were the first to adapt the Schnorr
protocol to achieve distance-bounding anonymous credentials. Their
approach has been shown to be vulnerable to \ac{DBDH} \cite{TamarinDB}.

  The Bussard-Bagga protocol also uses Schnorr, but slightly
  differently. It generates a sesson key, encrypts the private key
  with this session key. Then commits to each bit of the session key
  and each bit of the ciphertext. During the fast phase the verifier requests some bits from the session key and some from the ciphertext. Terrorist fraud is based on that knowing both session key and ciphertext one can compute the private key.
The prover then opens the commits, the verifier verifies them.
The prover and verifier run a PK that ties the commits to the private key.
A malicious prover can reduce all the N challenges in the fast phase
to 1. This allows both distance and terrorist
fraud~\cite{AttacksBussardBagga}.
